
\section{The Word}

ALCOHOLICS
ANONYMOUS
The Story of
How Many Thousands of Men and Women
Have Recovered from Alcoholism
FOURTH EDITION
ALCOHOLICS ANONYMOUS WORLD SERVICES, INC.
new york city
2001

\subsection{PREFACE}

This is the fourth edition of the book “Alcoholics Anonymous.”
The ﬁrst edition appeared in April 1939, and in the following sixteen years, more than 300,000 copies went into circulation.
The second edition, published in 1955, reached a total of more than 1,150,500 copies.
The third edition, which came off press in 1976, achieved a circulation of approximately 19,550,000 in all formats.

Because this book has become the basic text for our Society and has helped such large numbers of alcoholic men and women to recovery, there exists strong sentiment against any radical changes being made in it.
Therefore, the ﬁrst portion of this volume, describing the A.A. recovery program, has been left largely untouched in the course of revisions made for the second, third, and fourth editions.
The section called “The Doctor’s Opinion” has been kept intact, just as it was originally written in 1939 by the late Dr. William D. Silkworth, our Society’s great medical benefactor.
The second edition added the appendices, the Twelve Traditions, and the directions for getting in touch with A.A.
But the chief change was in the section of personal stories, which was expanded to reflect the Fellowship’s growth.
“Bill’s Story,” “Doctor Bob’s Nightmare,” and one other personal history from the first edition were retained intact; 
three were edited and one of these was retitled; 
new versions of two stories were written, with new titles; 
thirty completely new stories were added; 
and the story section was divided into three parts, under the same headings that are used now.

In the third edition, Part I (“Pioneers of A.A.”) was left unchanged.
Nine of the stories in Part II (“They Stopped in Time”) were carried over from the second edition; 
eight new stories were added.
In Part III (“They Lost Nearly All”), eight stories were retained; five new ones were added. 

This fourth edition includes the Twelve Concepts for World Service and revises the three sections of personal stories as follows.
One new story has been added to Part I, and two that originally appeared in Part III have been repositioned there; 
six stories have been deleted.
Six of the stories in Part II have been carried over, eleven new ones have been added, and eleven taken out.
Part III now includes twelve new stories; 
eight were removed (in addition to the two that were transferred to Part I).

All changes made over the years in the Big Book (A.A. members’ fond nickname for this volume) have had the same purpose: 
to represent the current membership of Alcoholics Anonymous more accurately, and thereby to reach more alcoholics.
If you have a drinking problem, we hope that you may pause in reading one of the forty-two personal stories and think: 
“Yes, that happened to me”; 
or, more important, “Yes, I’ve felt like that”; 
or, most important, “Yes, I believe this program can work for me too.”

%% xii


\subsection{FOREWORD TO SECOND EDITION}

Figures given in this foreword describe the
Fellowship as it was in 1955.

Since the original Foreword to this book was
written in 1939, a wholesale miracle has taken
place. Our earliest printing voiced the hope “that
every alcoholic who journeys will ﬁnd the Fellowship
of Alcoholics Anonymous at his destination. Already,”
continues the early text “twos and threes and ﬁves of
us have sprung up in other communities.”

Sixteen years have elapsed between our ﬁrst printing
of this book and the presentation in 1955 of our second
edition. In that brief space, Alcoholics Anonymous
has mushroomed into nearly 6,000 groups whose mem -
bership is far above 150,000 recovered alcoholics.
Groups are to be found in each of the United States
and all of the provinces of Canada. A.A. has ﬂourish -
ing communities in the British Isles, the Scandinavian
countries, South Africa, South America, Mexico,
Alaska, Australia and Hawaii. All told, promising
beginnings have been made in some 50 foreign coun-
tries and U. S. possessions. Some are just now taking
shape in Asia. Many of our friends encourage us by
 saying that this is but a beginning, only the augury of
a much larger future ahead.

The spark that was to ﬂare into the ﬁrst A.A. group
was struck at Akron, Ohio, in June 1935, during a talk
between a New York stockbroker and an Akron
physician. Six months earlier, the broker had been
relieved of his drink obsession by a sudden spiritual

%% xv

experience, following a meeting with an alcoholic
friend who had been in contact with the Oxford
Groups of that day. He had also been greatly helped
by the late Dr. William D. Silkworth, a New York
specialist in alcoholism who is now accounted no less
than a medical saint by A.A. members, and whose
story of the early days of our Society appears in the
next pages. From this doctor, the broker had learned
the grave nature of alcoholism. Though he could not
accept all the tenets of the Oxford Groups, he was
convinced of the need for moral inventory, confession
of personality defects, restitution to those harmed,
helpfulness to others, and the necessity of belief in and
dependence upon God.

Prior to his journey to Akron, the broker had worked
hard with many alcoholics on the theory that only an
alcoholic could help an alcoholic, but he had suc -
ceeded only in keeping sober himself. The broker had
gone to Akron on a business venture which had
collapsed, leaving him greatly in fear that he might
start drinking again. He suddenly realized that in
order to save himself he must carry his message to
another alcoholic. That alcoholic turned out to be
the Akron physician.

This physician had repeatedly tried spiritual means
to resolve his alcoholic dilemma but had failed. But
when the broker gave him Dr. Silkworth’s description
of alcoholism and its hopelessness, the physician began
to pursue the spiritual remedy for his malady with a
willingness he had never before been able to muster.
He sobered, never to drink again up to the moment of
his death in 1950. This seemed to prove that one
 alcoholic could affect another as no nonalcoholic

xvi

could. It also indicated that strenuous work, one
alcoholic with another, was vital to permanent re -
covery.

Hence the two men set to work almost frantically
upon alcoholics arriving in the ward of the Akron City
Hospital. Their very ﬁrst case, a desperate one, recov-
ered immediately and became A.A. number three. He
never had another drink. This work at Akron contin -
ued through the summer of 1935. There were many
failures, but there was an occasional heartening suc-
cess. When the broker returned to New York in the fall
of 1935, the ﬁrst A.A. group had actually been formed,
though no one realized it at the time.

A second small group promptly took shape at New
York, to be followed in 1937 with the start of a third at
Cleveland. Besides these, there were scattered al -
coholics who had picked up the basic ideas in Akron or
New York who were trying to form groups in other
cities. By late 1937, the number of members having
substantial sobriety time behind them was sufﬁcient to
convince the membership that a new light had en -
tered the dark world of the alcoholic.

It was now time, the struggling groups thought, to
place their message and unique experience before the
world. This determination bore fruit in the spring of
1939 by the publication of this volume. The member-
ship had then reached about 100 men and women. The
ﬂedgling society, which had been nameless, now began
to be called Alcoholics Anonymous, from the title of its
own book. The ﬂying-blind period ended and A.A. en-
tered a new phase of its pioneering time.
With the appearance of the new book a great deal
began to happen. Dr. Harry Emerson Fosdick, the

xvii

noted clergyman, reviewed it with approval. In the
fall of 1939 Fulton Oursler, then editor of Liberty,
printed a piece in his magazine, called “Alcoholics and
God.” This brought a rush of 800 frantic inquiries
into the little New York ofﬁce which meanwhile had
been established. Each inquiry was painstakingly
 answered; pamphlets and books were sent out. Busi -
nessmen, traveling out of existing groups, were
 referred to these prospective newcomers. New groups
started up and it was found, to the astonishment of
everyone, that A.A.’s message could be transmitted in
the mail as well as by word of mouth. By the end of
1939 it was estimated that 800 alcoholics were on
their way to recovery.

In the spring of 1940, John D. Rockefeller, Jr. gave
a dinner for many of his friends to which he invited
A.A. members to tell their stories. News of this got on
the world wires; inquiries poured in again and many
people went to the bookstores to get the book “Alco -
holics Anonymous.’’ By March 1941 the membership
had shot up to 2,000. Then Jack Alexander wrote a
 feature article in the Saturday Evening Post and
placed such a compelling picture of A.A. before the
general public that alcoholics in need of help really
 deluged us. By the close of 1941, A.A. numbered 8,000
members. The mushrooming process was in full swing.
A.A. had become a national institution.

Our Society then entered a fearsome and exciting
adolescent period. The test that it faced was this:
Could these large numbers of erstwhile erratic alco-
holics successfully meet and work together? Would
there be quarrels over membership, leadership, and
money? Would there be strivings for power and

%% xviii

prestige? Would there be schisms which would split
A.A. apart? Soon A.A. was beset by these very prob-
lems on every side and in every group. But out of this
frightening and at ﬁrst disrupting experience the con-
viction grew that A.A.’s had to hang together or die
separately. We had to unify our Fellowship or pass
off the scene.

As we discovered the principles by which the indi-
vidual alcoholic could live, so we had to evolve prin -
ciples by which the A.A. groups and A.A. as a whole
could survive and function effectively. It was thought
that no alcoholic man or woman could be excluded
from our Society; that our leaders might serve but
never govern; that each group was to be autonomous
and there was to be no professional class of therapy.
There were to be no fees or dues; our expenses were
to be met by our own voluntary contributions. There
was to be the least possible organization, even in our
service centers. Our public relations were to be based
upon attraction rather than promotion. It was decided
that all members ought to be anonymous at the level
of press, radio, TV and ﬁlms. And in no circumstances
should we give endorsements, make alliances, or enter
public controversies.

This was the substance of A.A.’s Twelve Traditions,
which are stated in full on page 561 of this book.
Though none of these principles had the force of rules
or laws, they had become so widely accepted by 1950
that they were conﬁrmed by our ﬁrst International
Conference held at Cleveland. Today the remarkable
unity of A.A. is one of the greatest assets that our
Society has.
While the internal difﬁculties of our adolescent

xix

period were being ironed out, public acceptance of
A.A. grew by leaps and bounds. For this there were two
principal reasons: the large numbers of recoveries, and
reunited homes. These made their impressions every-
where. Of alcoholics who came to A.A. and really tried,
50% got sober at once and remained that way; 25%  
sobered up after some relapses, and among the remainder,
those who stayed on with A.A. showed improvement.
Other thousands came to a few A.A. meet ings and at
ﬁrst decided they didn’t want the program. But great
numbers of these—about two out of three—began to
return as time passed.

Another reason for the wide acceptance of A.A. was
the ministration of friends—friends in medicine, reli-
gion, and the press, together with innumerable others
who became our able and persistent advocates. With -
out such support, A.A. could have made only the
 slowest progress. Some of the recommendations of
A.A.’s early medical and religious friends will be found
further on in this book.

Alcoholics Anonymous is not a religious organiza-
tion. Neither does A.A. take any particular medical
point of view, though we cooperate widely with the
men of medicine as well as with the men of religion.
Alcohol being no respecter of persons, we are an
accurate cross section of America, and in distant lands,
the same democratic evening-up process is now going
on. By personal religious afﬁliation, we include Catho -
lics, Protestants, Jews, Hindus, and a sprinkling of
Moslems and Buddhists. More than 15% of us are
women.

At present, our membership is pyramiding at the
rate of about twenty per cent a year. So far, upon the

\metapage(xx)

total problem of several million actual and potential
 alcoholics in the world, we have made only a scratch.
In all probability, we shall never be able to touch more
than a fair fraction of the alcohol problem in all its
 ramiﬁcations. Upon therapy for the alcoholic himself,
we surely have no monopoly. Yet it is our great hope
that all those who have as yet found no answer may
begin to ﬁnd one in the pages of this book and will
presently join us on the high road to a new freedom.

\metapage(xxi)


\subsection{FOREWORD TO THIRD EDITION}

By March 1976, when this edition went to the
printer, the total worldwide membership of
Alcoholics Anonymous was conservatively estimated at
more than 1,000,000, with almost 28,000 groups
meeting in over 90 countries.

Surveys of groups in the United States and Canada
indicate that A.A. is reaching out, not only to more
and more people, but to a wider and wider range.
Women now make up more than one-fourth of the
membership; among newer members, the proportion
is nearly one-third. Seven percent of the A.A.’s
surveyed are less than 30 years of age—among them,
many in their teens.

The basic principles of the A.A. program, it appears,
hold  good  for  individuals  with  many  dif -
ferent lifestyles, just as the program has brought
recovery to those of many different nationalities. The
Twelve Steps that summarize the program may be
called los Doce Pasos in one country, les Douze Etapes
in another, but they trace exactly the same path to
recovery that was blazed by the earliest members of
Alcoholics Anonymous.

In spite of the great increase in the size and the
span of this Fellowship, at its core it remains simple
and personal. Each day, somewhere in the world, re-
covery begins when one alcoholic talks with another
alcoholic, sharing experience, strength, and hope.

xxii


\subsection{FOREWORD TO FOURTH EDITION}

This fourth edition of “Alcoholics Anonymous”
came off press in November 2001, at the start of
a new millennium. Since the third edition was pub-
lished in 1976, worldwide membership of A.A. has just
about doubled, to an estimated two million or more,
with nearly 100,800 groups meeting in approximately
150 countries around the world. 
Literature has played a major role in A.A.’s growth,
and a striking phenomenon of the past quarter-
century has been the explosion of translations of our
basic literature into many languages and dialects. In
country after country where the A.A. seed was
planted, it has taken root, slowly at ﬁrst, then growing
by leaps and bounds when literature has become avail-
able. Currently, “Alcoholics Anonymous” has been
translated into forty-three* languages.

As the message of recovery has reached larger num-
bers of people, it has also touched the lives of a vastly
greater variety of suffering alcoholics. When the
phrase “We are people who normally would not mix”
(page 17 of this book) was written in 1939, it referred
to a Fellowship composed largely of men (and a few
women) with quite similar social, ethnic, and eco-
nomic backgrounds. Like so much of A.A.’s basic text,
those words have proved to be far more visionary than
the founding members could ever have imagined. The
stories added to this edition represent a membership
whose characteristics—of age, gender, race, and cul-
ture—have widened and have deepened to encompass

xxiii

*In 2013, Alcoholics Anonymous is in seventy languages.
virtually everyone the ﬁrst 100 members could have
hoped to reach.

While our literature has preserved the integrity of
the A.A. message, sweeping changes in society as a
whole are reﬂected in new customs and practices
within the Fellowship. Taking advantage of technolog-
ical advances, for example, A.A. members with com-
puters can participate in meetings online, sharing with
fellow alcoholics across the country or around the
world. In any meeting, anywhere, A.A.’s share experi-
ence, strength, and hope with each other, in order to
stay sober and help other alcoholics. Modem-to-
modem or face-to-face, A.A.’s speak the language of
the heart in all its power and simplicity.

xxiv

