
\biblebook{Spiritus}

\innerVerseHeading{'SPIRITUAL EXPERIENCE'}

\begin{biblechapter}
\verseWithHeading{Transformation}
    The terms "spiritual experience" 
    and "spiritual awakening" are used many times in this book 
    which, upon careful reading, 
    shows that the personality change 
    sufficient to bring about recovery from alcoholism has manifested
    itself among us in many different forms.

\verseWithHeading{Varieties}
Yet it is true that our first printing 
    gave many readers the impression that these personality changes, 
    or religious experiences, 
    must be in the nature of sudden and spectacular upheavals.
\verse Happily for everyone, this conclusion is erroneous.

\verse In the first few chapters 
    a number of sudden revolutionary changes are described.
\verse Though it was not our intention to create such an impression, 
    many alcoholics have nevertheless concluded that 
    in order to recover they must acquire an immediate and overwhelming 
    "God-consciousness" 
    followed at once by a vast change in feeling and outlook.
\end{biblechapter}

\begin{biblechapter}
\verseWithHeading{Educational Variety}
    Among our rapidly growing membership of thousands of alcoholics 
    such transformations, though frequent, are by no means the rule.
\verse Most of our experiences
    are what the psychologist William James calls 
    the "educational variety" 
    because they develop slowly over a period of time.
\verse Quite often friends of the newcomer are aware of the difference 
    long before he is himself.
\verse He finally realizes that he has undergone a profound alteration 
    in his reaction to life; 
    that such a change could hardly have been brought about 
    by himself alone.
\verse What often takes place in a few months 
    could hardly be accomplished by years of self-discipline.
\verse With few exceptions our members find 
    that they have tapped an unsuspected inner resource 
    which they presently identify with 
    their own conception of a Power greater than themselves.
 
\verseWithHeading{God-Consciousness}
Most of us think this awareness of a Power greater than ourselves 
    is the essence of spiritual experience.
\verse Our more religious members call it "God-consciousness."
\end{biblechapter}

\begin{biblechapter}
\verseWithHeading{Radical Honesty}
    Most emphatically we wish to say that 
    any alcoholic capable of honestly facing his problems 
    in the light of our experience 
    can recover, 
    provided he does not close his mind to all spiritual principles.
\verse He can only be defeated by an attitude of intolerance 
    or belligerent denial.

\verseWithHeading{Open Mindedness}
    We find that no one need have difficulty with 
    the spirituality of the program.
\verse WILLINGNESS, HONESTY AND OPEN MINDEDNESS ARE THE ESSENTIALS OF RECOVERY.
\verse BUT THESE ARE INDISPENSABLE.

\begin{quote}
\verse "There is a principle which is a bar against all information, 
    which is proof against all arguments 
    and which cannot fail to keep a man in everlasting ignorance--that 
    principle is contempt prior to investigation."

    \hfill{--HERBERT SPENCER}
\end{quote}
\end{biblechapter}

