\biblebook{Find}

\innerVerseHeading{'HOW TO GET IN TOUCH WITH A.A.'}

\begin{biblechapter}
\verseWithHeading{Localities}
    In the United States and Canada, 
    most towns and cities have A.A. groups.
\verse In such places, 
    A.A. can be located through the local telephone directory, 
    newspaper office,
    or police station, 
    or by contacting local priests or ministers.
\verse In large cities, 
    groups often maintain local offices 
    where alcoholics or their families 
    may arrange for interviews or hospitalization.
\verse These so-called intergroup associations are found under the listing 
    "A.A." or "Alcoholics Anonymous" in telephone directories.

\verseWithHeading{AAWS}
    At New York, U.S.A., 
    Alcoholics Anonymous maintains its international service center.
\verse The General Service Board of A.A. (the trustees) 
    administers A.A.'s General Service Office, A.A. World Services, Inc., 
    and our monthly magazine, the A.A. Grapevine.

\verse If you cannot find A.A. in your locality, 
    a letter addressed to Alcoholics Anonymous, 
    Box 459, Grand Central Station, New York, NY 10163, U.S.A., 
    will receive a prompt reply from this world center, 
    referring you to the nearest A.A. group.
\verse If there is none nearby, 
    you will be invited to carry on a correspondence 
    which will do much to insure your sobriety 
    no matter how isolated you are.

\verseWithHeading{AL-ANON}
    Should you be the relative or friend of an alcoholic 
    who shows no immediate interest in A.A., 
    it is suggested that you write the Al-Anon Family Groups, Inc., 
    P. O. Box 862, Midtown Station, New York, NY 10018, U.S.A.

\verse This is a world clearing house for the Al-Anon Family Groups, 
    composed largely of the wives, husbands and friends of A.A. members.
\verse This headquarters will give the location of the nearest Family Group 
    and will, if you wish, correspond with you about your special problems.
\end{biblechapter}
