
\biblebook{Blessings}

\subsection*{THE RELIGIOUS VIEW ON A.A.}

\begin{biblechapter}
\verseWithHeading{}
    Clergymen of practically every denomination 
    have given A.A. their blessing.

\verseWithHeading{Ed}
    Edward Dowling, S.J.,
    \footnote[*]{Father Ed, an early and wonderful friend of A.A., died in the Spring of 1960.}
    of the Queen's Work staff says,
\verse\emph{ "Alcoholics Anonymous is natural; 
    it is natural at the point where nature 
    comes closest to the supernatural,
    namely in humiliations and in consequent humility.
\verse There is something spiritual about an art museum or a symphony, 
    and the Catholic Church approves of our use of them.
\verse There is something spiritual about A.A. too, 
    and Catholic participation in it almost invariably results 
    in poor Catholics becoming better Catholics."
}

\verseWithHeading{THE LIVING CHURCH}
    The Episcopal magazine, THE LIVING CHURCH, observes editorially: 
\verse\emph{ "The basis of the technique of Alcoholics Anonymous 
    is the truly Christian principle 
    that a man cannot help himself except by helping others.
    The A.A. plan is described by the members themselves as 
    'self-insurance.'
\verse This self-insurance has resulted in the restoration of 
    physical, mental and spiritual health 
    and self-respect to hundreds of man and women 
    who would be hopelessly down and out 
    without its unique but effective therapy."
}

\verseWithHeading{Emerson}
    Speaking at a dinner given by Mr. John D. Rockefeller 
    to introduce Alcoholics Anonymous to some of his friends,
    Dr. Harry Emerson Fosdick remarked:

\verse\emph{"I think that psychologically speaking 
    there is a point of advantage 
    in the approach that is being made in this movement 
    that cannot be duplicated.
\verse I suspect that if it is wisely handled--and 
    it seems to be in wise and prudent hands--there 
    are doors of opportunity ahead of this project 
    that may surpass our capacities to imagine."
}


\end{biblechapter}
