\begin{fmatterchapter}

\biblebook[Editorial Note]{Editorial Note}

\begin{center}[ EARLY DRAFT STATE ]\end{center}

This work transforms the presentation of the Basic Texts 
    into verse form 
    in the manner which is typically implemented 
    within spiritual study.

In this instance we have taken the form of 'Book Chapter:Verse', 
    where what were previously chapters are now recategorised as books.
This does not change the original text in any way, 
    it is a simple heuristic reorganisation 
    to assist a more intuitive reference to the parts of the text.
In fact, 
    the length of a chapter in our original basic text presentation 
    often corresponds to the length of a book 
    in other spiritual domains of study.

The new 'Chapter' heuristic 
    is a means of slicing up the text into shorter sets of paragraphs.
As has been mentioned, the text is dense, 
    and reading a single paragraph of it 
    can sometimes be the substance of a whole meeting.
The original chapters are lengthy, 
    and contain unmarked subsections 
    which are quite distinctly different thematically.
The redefining of the chapter heuristic 
    will intend to draw boundaries where distinct thematic shifts occur.

The 'Verse', for the time being, has generally come to refer to sentences.
Although verses are commonly more general than sentences, 
    perhaps referring to units of referencable meaning, 
    and so could iterate mid sentence, 
    or even over multiple sentences, 
    depending on the depth of ideas being laid out.
For the time being, 
    the boundary has been drawn pragmatically at the level of sentence.

The generation of the new heuristics of 'Chapter' and 'Verse' 
    will be an ongoing project,
    involving incremental discernment of precise thematic shifts,
    which will necessarily involve subjective interpretation
    and a great deal of time.

% TODO - examples of key excerpts such as promises, how it works, end of into action. But first complete the versification of those parts.

\end{fmatterchapter}
