
\biblebook{Solution}

\bbHeading{BB. THERE IS A SOLUTION p. 17-29}
\bbChapterPreamble


\begin{biblechapter}
\verseWithHeading{Hope}
    We, of Alcoholics Anonymous, 
    know thousands of men and women who were once just as hopeless as Bill. 
\verse Nearly all have recovered. 
\verse They have solved the drink problem.

\verseWithHeading{Who we are}
    We are average Americans. 
\verse All sections of this country 
    and many of its occupations are represented, 
    as well as many political, economic, social, 
    and religious backgrounds. 
\verse We are people who normally would not mix. 
\verse But there exists among us a fellowship, 
    a friendliness, 
    and an understanding which is indescribably wonderful. 
\verse We are like the passengers of a great liner 
    the moment after rescue from shipwreck when 
    camaraderie, joyousness and democracy pervade the vessel 
    from steerage to Captain's table. 
\verse Unlike the feelings of the ship's passengers, however, 
    our joy in escape from disaster does not subside 
    as we go our individual ways. 
\verse The feeling of having shared in a common peril is one element 
    in the powerful cement which binds us. 
\verse But that in itself would never have held us together 
    as we are now joined.

\verseWithHeading{Solution}
    The tremendous fact for every one of us is 
    that we have discovered a common solution. 
\verse We have a way out on which we can absolutely agree, 
    and upon which we can join in brotherly and harmonious action. 
\verse This is the great news this book carries 
    to those who suffer from alcoholism. 
\verse An illness of this sort 
    and we have come to believe it an illness 
    involves those about us in a way no other human sickness can. 
\verse If a person has cancer all are sorry for him 
    and no one is angry or hurt. 
\verse But not so with the alcoholic illness, 
    for with it there goes annihilation 
    of all the things worth while in life. 
\verse It engulfs all whose lives touch the sufferer's. 
\verse It brings misunderstanding, 
    fierce resentment, 
    financial insecurity, 
    disgusted friends and employers, 
    warped lives of blameless children, 
    sad wives and parents anyone can increase the list.

\verse We hope this volume will inform and comfort those who are, 
    or who may be affected. 
\verse There are many.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Shared Experience}
    Highly competent psychiatrists who have dealt with us 
    have found it sometimes impossible to persuade an alcoholic 
    to discuss his situation without reserve. 
\verse Strangely enough, wives, parents and intimate friends 
    usually find us even more unapproachable 
    than do the psychiatrist and the doctor.

\verse But the ex-problem drinker who has found this solution, 
    who is properly armed with facts about himself, 
    can generally win the entire confidence of another alcoholic 
    in a few hours. 
\verse Until such an understanding is reached, 
    little or nothing can be accomplished.

\verse That the man who is making the approach has had the same difficulty, 
    that he obviously knows what he is talking about, 
    that his whole deportment shouts at the new prospect 
    that he is a man with a real answer, 
    that he has no attitude of Holier Than Thou, 
    nothing whatever except the sincere desire to be helpful; 
    that there are no fees to pay, 
    no axes to grind, 
    no people to please, 
    no lectures to be endured 
    these are the conditions we have found most effective. 
\verse After such an approach many take up their beds and walk again.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Carrying The Message}
    None of us makes a sole vocation of this work, 
    nor do we think its effectiveness would be increased if we did. 
\verse We feel that elimination of our drinking is but a beginning. 
\verse A much more important demonstration of our principles 
    lies before us in our respective homes, occupations and affairs. 
\verse All of us spend much of our spare time 
    in the sort of effort which we are going to describe. 
\verse A few are fortunate enough to be so situated 
    that they can give nearly all their time to the work.

\verse If we keep on the way we are going 
    there is little doubt that much good will result, 
    but the surface of the problem would hardly be scratched. 
\verse Those of us who live in large cities 
    are overcome by the reflection that close by 
    hundreds are dropping into oblivion every day. 
\verse Many could recover if they had the opportunity we have enjoyed. 
\verse How then shall we present that which has been so freely given us?

\verse We have concluded to publish an anonymous volume 
    setting forth the problem as we see it. 
\verse We shall bring to the task our combined experience and knowledge. 
\verse This should suggest a useful program 
    for anyone concerned with a drinking problem.

\verse Of necessity there will have to be discussion 
    of matters medical, psychiatric, social, and religious. 
\verse We are aware that these matters are from their very nature, controversial. 
\verse Nothing would please us so much as to write a book 
    which would contain no basis for contention or argument. 
\verse We shall do our utmost to achieve that ideal. 
\verse Most of us sense that real tolerance 
    of other people's shortcomings and viewpoints 
    and a respect for their opinions 
    are attitudes which make us more useful to others. 
\verse Our very lives, as ex-problem drinkers, 
    depend upon our constant thought of others 
    and how we may help meet their needs.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Who Me?}
    You may already have asked yourself 
    why it is that all of us became so very ill from drinking. 
\verse Doubtless you are curious to discover how and why, 
    in the face of expert opinion to the contrary, 
    we have recovered from a hopeless condition of mind and body. 
\verse If you are an alcoholic who wants to get over it, 
    you may already be asking 
    "What do I have to do?"

\verse It is the purpose of this book 
    to answer such questions specifically. 
\verse We shall tell you what we have done. 
\verse Before going into a detailed discussion, 
    it may be well to summarize some points as we see them.

\verse How many time people have said to us: 
\verse "I can take it or leave it alone. Why can't he?" 
\verse "Why don't you drink like a gentleman or quit?" 
\verse "That fellow can't handle his liquor." 
\verse "Why don't you try beer and wine?" 
\verse "Lay off the hard stuff." 
\verse "His will power must be weak." 
\verse "He could stop if he wanted to." 
\verse "She's such a sweet girl, I should think he'd stop for her sake." 
\verse "The doctor told him that 
    if he ever drank again it would kill him, 
    but there he is all lit up again."

\verse Now these are commonplace observations on drinkers 
    which we hear all the time. 
\verse Back of them is a world of ignorance and misunderstanding. 
\verse We see that these expressions refer to people 
    whose reactions are very different from ours.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Non-Alcoholics}
\verse Moderate drinkers have little trouble in giving up liquor entirely 
    if they have good reason for it. 
\verse They can take it or leave it alone.

\verse Then we have a certain type of hard drinker. 
\verse He may have the habit badly enough to gradually impair him 
    physically and mentally. 
\verse It may cause him to die a few years before his time. 
\verse If a sufficiently strong reason 
    ill health, falling in love, change of environment, 
    or the warning of a doctor becomes operative, 
    this man can also stop or moderate, 
    although he may find it difficult and troublesome 
    and may even need medical attention.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{The Alcoholic}
    But what about the real alcoholic? 
\verse He may start off as a moderate drinker; 
    he may or may not become a continuous hard drinker; 
    but at some stage of his drinking career 
    he begins to lose all control of his liquor consumption, 
    once he starts to drink.

\verse Here is a fellow who has been puzzling you, 
    especially in his lack of control. 
\verse He does absurd, incredible, tragic things while drinking. 
\verse He is a real Dr. Jekyll and Mr. Hyde. 
\verse He is seldom mildly intoxicated. 
\verse He is always more or less insanely drunk. 
\verse His disposition while drinking 
    resembles his normal nature but little. 
\verse He may be one of the finest fellows in the world. 
\verse Yet let him drink for a day, 
    and he frequently becomes disgustingly, 
    and even dangerously anti-social. 
\verse He has a positive genius for 
    getting tight at exactly the wrong moment, 
    particularly when some important decision must be made 
    or engagement kept. 
\verse He is often perfectly sensible and well balanced 
    concerning everything except liquor, 
    but in that respect he is incredibly dishonest and selfish. 
\verse He often possesses special abilities, skills, and aptitudes, 
    and has a promising career ahead of him. 
\verse He uses his gifts to build up a bright outlook 
    for his family and himself, 
    and then pulls the structure down on his head 
    by a senseless series of sprees. 
\verse He is the fellow who goes to bed so intoxicated 
    he ought to sleep the clock around. 
\verse Yet early next morning he searches madly 
    for the bottle he misplace the night before. 
\verse If he can afford it, 
    he may have liquor concealed all over his house 
    to be certain no one gets his entire supply away from him 
    to throw down the wastepipe. 
\verse As matters grow worse, 
    he begins to use a combination of high-powered sedative and liquor 
    to quiet his nerves so he can go to work. 
\verse Then comes the day when he simply cannot make it 
    and gets drunk all over again. 
\verse Perhaps he goes to a doctor who gives him morphine 
    or some sedative with which to taper off. 
\verse Then he begins to appear at hospitals and sanitariums.

\verse This is by no means a comprehensive picture of the true alcoholic, 
    as our behavior patterns vary. 
\verse But this description should identify him roughly.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Powerlessness}
    Why does he behave like this? 
\verse If hundreds of experiences have shown him 
    that one drink means another debacle 
    with all its attendant suffering and humiliation, 
    why is it he takes that one drink? 
\verse Why can't he stay on the water wagon? 
\verse What has become of the common sense and will power 
    that he still sometimes displays with respect to other matters?

\verse Perhaps there never will be a full answer to these questions. 
\verse Opinions vary considerably as to why the alcoholic 
    reacts differently from normal people. 
\verse We are not sure why, 
    once a certain point is reached, 
    little can be done for him. 
\verse We cannot answer the riddle.

\verse We know that while the alcoholic keeps away from drink, 
    as he may do for months or years, 
    he reacts much like other men. 
\verse We are equally positive that once he takes any alcohol 
    whatever into his system, something happens, 
    both in the bodily and mental sense, 
    which makes it virtually impossible for him to stop. 
\verse The experience of any alcoholic will abundantly confirm this.

\verse These observations would be academic and pointless 
    if our friend never took the first drink, 
    thereby setting the terrible cycle in motion. 
\verse Therefore, the main problem of the alcoholic centers in his mind, 
    rather than in his body. 
\verse If you ask him why he started on that last bender, 
    the chances are he will offer you any one of a hundred alibis. 
\verse Sometimes these excuses have a certain plausibility, 
    but none of them really makes sense 
    in the light of the havoc an alcoholic's drinking bout creates. 
\verse They sound like the philosophy of the man who, having a headache, 
    beats himself on the head with a hammer so that he can't feel the ache. 
\verse If you draw this fallacious reasoning 
    to the attention of an alcoholic, 
    he will laugh it off, 
    or become irritated and refuse to talk.

\verse Once in a while he may tell the truth. 
\verse And the truth, strange to say, 
    is usually that he has no more idea why he took that first drink 
    than you have. 
\verse Some drinkers have excuses with which they are satisfied part of the time. 
\verse But in their hearts they really do not know why they do it. 
\verse Once this malady has a real hold, they are a baffled lot. 
\verse There is the obsession that somehow, someday, 
    they will beat the game. 
\verse But they often suspect they are down for the count.

\verse How true this is, few realize. 
\verse In a vague way their families and friends sense 
    that these drinkers are abnormal, 
    but everybody hopefully awaits the day 
    when the sufferer will rouse himself from his lethargy 
    and assert his power of will.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Unmanageability}
    The tragic truth is that if the man be a real alcoholic, 
    the happy day may not arrive. 
\verse He has lost control. 
\verse At a certain point in the drinking of every alcoholic, 
    he passes into a state where the most powerful desire to stop drinking 
    is of absolutely no avail. 
\verse This tragic situation has already arrived 
    in practically every case long before it is suspected.

\verse The fact is that most alcoholics, 
    for reasons yet obscure, 
    have lost the power of choice in drink. 
\verse Our so called will power becomes practically nonexistent. 
\verse We are unable, at certain times, 
    to bring into our consciousness with sufficient force 
    the memory of the suffering and humiliation 
    of even a week or a month ago. 
\verse We are without defense against the first drink.

\verse The almost certain consequences 
    that follow taking even a glass of beer 
    do not crowd into the mind to deter us. 
\verse If these thoughts occur, 
    they are hazy and readily supplanted with the old threadbare idea 
    that this time we shall handle ourselves like other people. 
\verse There is a complete failure of the kind of defense 
    that keeps one from putting his hand on a hot stove.

\verse The alcoholic may say to himself in the most casual way, 
    "It won't burn me this time, so here's how!". 
\verse Or perhaps he doesn't think at all. 
\verse How often have some of us begun to drink in this nonchalant way, 
    and after the third or fourth, 
    pounded on the bar and said to ourselves, 
    "For God's sake, how did I ever get started again?". 
\verse Only to have that thought supplanted by 
    "Well, I'll stop with the sixth drink." 
\verse Or "What's the use anyhow?"

\verse When this sort of thinking 
    is fully established in an individual with alcoholic tendencies, 
    he has probably placed himself beyond human aid, 
    and unless locked up, may die or go permanently insane. 
\verse These stark and ugly facts have been confirmed 
    by legions of alcohoholics throughout history. 
\verse But for the grace of God, 
    there would have been thousands more convincing demonstrations. 
\verse So many want to stop but cannot.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{There is a Solution}
    There is a solution. 
\verse Almost none of us liked the self-searching, 
    the leveling of our pride, the confession of shortcomings 
    which the process requires for its successful consummation. 
\verse But we saw that it really worked in others, 
    and we had come to believe in the hopelessness 
    and futility of life as we had been living it. 
\verse When, therefore, 
    we were approached by those in whom the problem had been solved, 
    there was nothing left for us 
    but to pick up the simple kit of spiritual tools 
    laid at out feet. 
\verse We have found much of heaven 
    and we have been rocketed into a fourth dimension of existence 
    of which we had not even dreamed.

\verse The great fact is just this, and nothing less: 
\verse That we have had deep and effective spiritual experiences* 
    which have revolutionized our whole attitude toward life, 
    toward our fellows 
    and toward God's universe. 
\verse The central fact of our lives today is the absolute certainty 
    that our Creator has entered into our hearts and lives 
    in a way which is indeed miraculous. 
\verse He has commenced to accomplish those things for us 
    which we could never do by ourselves.

\verse If you are as seriously alcoholic as we were, 
    we believe there is no middle-of-the-road solution. 
\verse We were in a position where life was becoming impossible, 
    and if we had passed into the region from which 
    there is no return through human aid, 
    we had but two alternatives: 
\verse One was to go on to the bitter end, 
    blotting out the consciousness of our intolerable situation 
    as best we could; 
    and the other, to accept spiritual help. 
\verse This we did because we honestly wanted to, 
    and were willing to make the effort.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Hazard}
    A certain American business man had ability, 
    good sense, 
    and high character. 
\verse For years he had floundered from one sanitarium to another. 
\verse He had consulted the best known American psychiatrists. 
\verse Then he had gone to Europe, 
    placing himself in the care of a celebrated physician 
    (the psychiatrist, Dr. Jung) 
    who prescribed for him. 
\verse Though experience had made him skeptical, 
    he finished his treatment with unusual confidence. 
\verse His physical and mental condition were unusually good. 
\verse Above all, he believed he had acquired such a profound knowledge 
    of the inner workings of his mind 
    and its hidden springs that relapse was unthinkable. 
\verse Nevertheless, he was drunk in a short time. 
\verse More baffling still, 
    he could give himself no satisfactory explanation for his fall.

\verse So he returned to this doctor, whom he admired, 
    and asked him point-blank why he could not recover. 
\verse He wished above all things to regain self-control. 
\verse He seemed quite rational and well-balanced 
    with respect to other problems. 
\verse Yet he had no control whatever over alcohol. 
\verse Why was this?

\verse He begged the doctor to tell him the whole truth, and he got it. 
\verse In the doctor's judgment he was utterly hopeless; 
    he could never regain his position in society 
    and he would have to place himself under lock and key 
    or hire a bodyguard if he expected to live long. 
\verse That was a great physician's opinion.

\verse But this man still lives, and is a free man. 
\verse He does not need a bodyguard nor is he confined. 
\verse He can go anywhere on this earth 
    where other free men may go without disaster, 
    provided he remains willing to maintain a certain simple attitude.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Jung}
    Some of our alcoholic readers may think 
    they can do without spiritual help. 
\verse Let us tell you the rest of the conversation our friend had 
    with his doctor.

\verse The doctor said: \emph{
"You have the mind of a chronic alcoholic. 
\verse I have never seen one single case recover, 
    where that state of mind existed to the extent that it does in you." 
}
\verse Our friend felt as though 
    the gates of hell had closed on him with a clang.

\verse He said to the doctor, "Is there no exception?"

\emph{
\verse "Yes," replied the doctor, 
    "there is. 
\verse Exceptions to cases such as yours 
    have been occurring since early times. 
\verse Here and there, once in a while, 
    alcoholics have had what are called vital spiritual experiences. 
\verse To me these occurrences are phenomena. 
\verse They appear to be in the nature of 
    huge emotional displacements and rearrangements. 
\verse Ideas, emotions, and attitudes 
    which were once the guiding forces of the lives of these men 
    are suddenly cast to one side, 
    and a completely new set of conceptions and motives 
    begin to dominate them. 
\verse In fact, I have been trying to produce 
    some such emotional rearrangement within you. 
\verse With many individuals the methods which I employed are successful, 
    but I have never been successful with an alcoholic of your description."
}

\verse Upon hearing this, 
    our friend was somewhat relieved, 
    for he reflected that, after all, 
    he was a good church member. 
\verse This hope, however, was destroyed 
    by the doctor's telling him 
    that while his religious convictions were very good, 
    in his case they did not spell the necessary vital spiritual experience.

\verse Here was the terrible dilemma 
    in which our friend found himself 
    when he had the extraordinary experience, 
    which as we have already told you, made him a free man.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{James}
    We, in our turn, 
    sought the same escape with all the desperation of drowning men. 
\verse What seemed at first a flimsy reed, 
    has proved to be the loving and powerful hand of God. 
\verse A new life has been given us or, if you prefer, 
    "a design for living" that really works.

\verse The distinguished American psychologist, William James, 
    in his book "Varieties of Religious Experience," 
    indicates a multitude of ways in which men have discovered God. 
\verse We have no desire to convince anyone that there is only one way 
    by which faith can be acquired. 
\verse If what we have learned and felt and seen means anything at all, 
    it means that all of us, whatever our race, creed, or color 
    are the children of a living Creator 
    with whom we may form a relationship 
    upon simple and understandable terms 
    as soon as we are willing and honest enough to try. 
\verse Those having religious affiliations 
    will find here nothing disturbing to their beliefs or ceremonies. 
\verse There is no friction among us over such matters.

\verse We think it no concern of ours what religious bodies 
    our members identify themselves with as individuals. 
\verse This should be an entirely personal affair 
    which each one decides for himself 
    in the light of past associations, or his present choice. 
\verse Not all of us join religious bodies, 
    but most of us favor such memberships.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Bigbook Arc}
    In the following chapter, 
    there appears an explanation of alcoholism, 
    as we understand it, 
    then a chapter addressed to the agnostic. 
\verse Many who once were in this class are now among our members. 
\verse Surprisingly enough, 
    we find such convictions no great obstacle to a spiritual experience.

\verse Further on, clear-cut directions are given showing how we recovered. 
\verse These are followed by three dozen personal experiences.

\verse Each individual, in the personal stories, 
    describes in his own language 
    and from his own point of view 
    the way he established his relationship with God. 
\verse These give a fair cross section of our membership 
    and a clear-cut idea of what has actually happened in their lives.

\verse We hope no one will consider these self-revealing accounts in bad taste. 
\verse Our hope is that many alcoholic men and women, 
    desperately in need, will see these pages, 
    and we believe that it is only by fully disclosing ourselves 
    and our problems 
    that they will be persuaded to say, 
    "Yes, I am one of them too; I must have this thing."
\end{biblechapter}
