\biblebook{Bill}

\bbHeading{BB. BILL'S STORY p. 1-16}
\bbChapterPreamble


\begin{biblechapter}
\verseWithHeading{Beginnings}
    WAR FEVER ran high in the New England town 
    to which we new, young officers from Plattsburg were assigned, 
    and we were flattered when the first citizens took us to their homes, 
    making us feel heroic.
\verse Here was love, applause, war; 
    moments sublime with intervals hilarious.
\verse I was part of life at last, 
    and in the midst of the excitement I discovered liquor.
\verse I forgot the strong warnings 
    and the prejudices of my people concerning drink.
\verse In time we sailed for "Over There."
\verse I was very lonely and again turned to alcohol.

\verse We landed in England.
\verse I visited Winchester Cathedral.
\verse Much moved, I wandered outside.
\verse My attention was caught by a doggerel on an old tombstone:

\verse\begin{quote}"Here lies a Hampshire Grenadier.
    
    Who caught his death.
    
    Drinking cold small beer.
    
    A good soldier is ne'er forgot.
    
    Whether he dieth by musket.
    
    Or by pot."\end{quote}

\verse Ominous warning-which I failed to heed.

\verse Twenty-two, and a veteran of foreign wars, I went home at last.
\verse I fancied myself a leader, 
    for had not the men of my battery 
    given me a special token of appreciation?
\verse My talent for leadership, I imagined, 
    would place me at the head of vast enterprises 
    which I would manage with the utmost assurance.

\verse I took a night law course, 
    and obtained employment as investigator for a surety company.
\verse The drive for success was on.
\verse I'd prove to the world I was important.
\verse My work took me about Wall Street 
    and little by little I became interested in the market.
\verse Many people lost money-but some became very rich.
\verse Why not I?
\verse I studied economics and business as well as law.
\verse Potential alcoholic that I was, I nearly failed my law course.
\verse At one of the finals I was too drunk to think or write.
\verse Though my drinking was not yet continuous, it disturbed my wife.
\verse We had long talks when I would still her forebodings 
    by telling her that men of genius 
    conceived their best projects when drunk; 
    that the most majestic constructions of philosophic thought 
    were so derived.

\verse By the time I had completed the course, 
    I knew the law was not for me.
\verse The inviting maelstrom of Wall Street had me in its grip.
\verse Business and financial leaders were my heroes.
\verse Out of this alloy of drink and speculation, 
    I commenced to forge the weapon that one day would turn in its flight 
    like a boomerang and all but cut me to ribbons.
\verse Living modestly, my wife and I saved \$1,000.
\verse It went into certain securities, then cheap and rather unpopular.
\verse I rightly imagined that they would some day have a great rise.
\verse I failed to persuade my broker friends to send me out looking over factories and managements, 
    but my wife and I decided to go anyway.
\verse I had developed a theory that most people lost money in stocks through ignorance of markets.
\verse I discovered many more reasons later on.

\verse We gave up our positions and off we roared on a motorcycle, 
    the sidecar stuffed with tent, blankets, a change of clothes, 
    and three huge volumes of a financial reference service.
\verse Our friends thought a lunacy commission should be appointed.
\verse Perhaps they were right.
\verse I had had some success at speculation, 
    so we had a little money, 
    but we once worked on a farm for a month to avoid drawing on our small capital.
\verse That was the last honest manual labor on my part for many a day.
\verse We covered the whole eastern United States in a year.
\verse At the end of it, 
    my reports to Wall Street procured me a position there 
    and the use of a large expense account.
\verse The exercise of an option brought in more money, 
    leaving us with a profit of several thousand dollars for that year.

\verse For the next few years fortune threw money and applause my way.
\verse I had arrived.
\verse My judgment and ideas were followed by many to the tune of paper millions.
\verse The great boom of the late twenties was seething and swelling.
\verse Drink was taking an important and exhilarating part in my life.
\verse There was loud talk in the jazz places uptown.
\verse Everyone spent in thousands and chattered in millions.
\verse Scoffers could scoff and be damned.
\verse I made a host of fair-weather friends.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{The Fall}
    My drinking assumed more serious proportions, 
    continuing all day and almost every night.
\verse The remonstrances of my friends terminated in a row and I became a lone wolf.
\verse There were many unhappy scenes in our sumptuous apartment.
\verse There had been no real infidelity, 
    for loyalty to my wife, 
    helped at times by extreme drunkenness, 
    kept me out of those scrapes.

\verse In 1929 I contracted golf fever.
\verse We went at once to the country, 
    my wife to applaud while I started out to overtake Walter Hagen.
\verse Liquor caught up with me much faster than I came up behind Walter.
\verse I began to be jittery in the morning.
\verse Golf permitted drinking every day and every night.
\verse It was fun to carom around the exclusive course 
    which had inspired such awe in me as a lad.
\verse I acquired the impeccable coat of tan one sees upon the well-to-do.
\verse The local banker watched me whirl fat checks in and out of his till with amused skepticism.

\verse Abruptly in October 1929 hell broke loose on the New York stock exchange.
\verse After one of those days of inferno, 
    I wobbled from a hotel bar to a brokerage office.
\verse It was eight o'clock-five hours after the market closed.
\verse The ticker still clattered.
\verse I was staring at an inch of the tape which bore the inscription XYZ-32.
\verse It had been 52 that morning.
\verse I was finished and so were many friends.
\verse The papers reported men jumping to death from the towers of High Finance.
\verse That disgusted me.
\verse I would not jump.
\verse I went back to the bar.
\verse My friends had dropped several million since ten o'clock-so what?
\verse Tomorrow was another day.
\verse As I drank, the old fierce determination to win came back.

\verse Next morning I telephoned a friend in Montreal.
\verse He had plenty of money left and thought I had better go to Canada.
\verse By the following spring we were living in our accustomed style.
\verse I felt like Napoleon returning from Elba.
\verse No St. Helena for me!
\verse But drinking caught up with me again and my generous friend had to let me go.
\verse This time we stayed broke.

\verse We went to live with my wife's parents.
\verse I found a job; 
    then lost it as the result of a brawl with a taxi driver.
\verse Mercifully, no one could guess that I was to have no real employment for five years, 
    or hardly draw a sober breath.
\verse My wife began to work in a department store, 
    coming home exhausted to find me drunk.

\verse I became an unwelcome hanger-on at brokerage places.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Manageable}
    Liquor ceased to be a luxury; 
    it became a necessity.
\verse "Bathtub" gin, two bottles a day, and often three, got to be routine.
\verse Sometimes a small deal would net a few hundred dollars, 
    and I would pay my bills at the bars and delicatessens.
\verse This went on endlessly, 
    and I began to waken very early in the morning shaking violently.
\verse A tumbler full of gin followed by half a dozen bottles of beer 
    would be required if I were to eat any breakfast.
\verse Nevertheless, I still thought I could control the situation, 
    and there were periods of sobriety which renewed my wife's hope.

\verse Gradually things got worse.
\verse The house was taken over by the mortgage holder, 
    my mother-in-law died, 
    my wife and father-in-law became ill.

\verse Then I got a promising business opportunity.
\verse Stocks were at the low point of 1932, 
    and I had somehow formed a group to buy.
\verse I was to share generously in the profits.
\verse Then I went on a prodigious bender, and that chance vanished.

\verse I woke up.
\verse This had to be stopped. 
\verse I saw I could not take so much as one drink.
\verse I was through forever.
\verse Before then, I had written lots of sweet promises, 
    but my wife happily observed that this time I meant business.
\verse And so I did.

\verse Shortly afterward I came home drunk.
\verse There had been no fight.
\verse Where had been my high resolve?
\verse I simply didn't know.
\verse It hadn't even come to mind.
\verse Someone had pushed a drink my way, and I had taken it.
\verse Was I crazy?
\verse I began to wonder, 
    for such an appalling lack of perspective seemed near being just that.

\verse Renewing my resolve, I tried again.
\verse Some time passed, and confidence began to be replaced by cock-sureness.
\verse I could laugh at the gin mills.
\verse Now I had what it takes!
\verse One day I walked into a cafe to telephone.
\verse In no time I was beating on the bar asking myself how it happened.
\verse As the whisky rose to my head I told myself I would manage better next time, 
    but I might as well get good and drunk then.
\verse And I did.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Powerlessness}
    The remorse, horror and hopelessness of the next morning are unforgettable.
\verse The courage to do battle was not there.
\verse My brain raced uncontrollably 
    and there was a terrible sense of impending calamity.
\verse I hardly dared cross the street, 
    lest I collapse and be run down by an early morning truck, 
    for it was scarcely daylight.
\verse An all night place supplied me with a dozen glasses of ale.
\verse My writhing nerves were stilled at last.
\verse A morning paper told me the market had gone to hell again.
\verse Well, so had I.
\verse The market would recover, but I wouldn't.
\verse That was a hard thought.
\verse Should I kill myself?
\verse No-not now.
\verse Then a mental fog settled down.
\verse Gin would fix that.
\verse So two bottles, and-oblivion.

\verse The mind and body are marvelous mechanisms, 
    for mine endured this agony two more years.
\verse Sometimes I stole from my wife's slender purse 
    when the morning terror and madness were on me.
\verse Again I swayed dizzily before an open window, 
    or the medicine cabinet where there was poison, 
    cursing myself for a weakling.
\verse There were flights from city to country and back, 
    as my wife and I sought escape.
\verse Then came the night when the physical and mental torture was so hellish 
    I feared I would burst through my window, sash and all.
\verse Somehow I managed to drag my mattress to a lower floor, lest I suddenly leap.
\verse A doctor came with a heavy sedative.
\verse Next day found me drinking both gin and sedative.
\verse This combination soon landed me on the rocks.
\verse People feared for my sanity.
\verse So did I.
\verse I could eat little or nothing when drinking, and I was forty pounds under weight.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Silkworth}
    My brother-in-law is a physician, 
    and through his kindness and that of my mother 
    I was placed in a nationally-known hospital 
    for the mental and physical rehabilitation of alcoholics.
\verse Under the so-called belladonna treatment my brain cleared.
\verse Hydrotherapy and mild exercise helped much.
\verse Best of all, 
    I met a kind doctor who explained that though certainly selfish and foolish, 
    I had been seriously ill, 
    bodily and mentally.

\verse It relieved me somewhat to learn that in alcoholics 
    the will is amazingly weakened when it comes to combating liquor, 
    though it often remains strong in other respects.
\verse My incredible behavior in the face of a desperate desire to stop was explained.
\verse Understanding myself now, I fared forth in high hope.
\verse For three or four months the goose hung high.
\verse I went to town regularly and even made a little money.
\verse Surely this was the answer-self-knowledge.

\verse But it was not, for the frightful day came when I drank once more.
\verse The curve of my declining moral and bodily health fell off like a ski-jump.
\verse After a time I returned to the hospital.
\verse This was the finish, the curtain, it seemed to me.
\verse My weary and despairing wife was informed that 
    it would all end with heart failure during delirium tremens, 
    or I would develop a wet brain, perhaps within a year.
\verse She would soon have to give me over to the undertaker or the asylum.

\verse They did not need to tell me.
\verse I knew, and almost welcomed the idea.
\verse It was a devastating blow to my pride.
\verse I, who had thought so well of myself and my abilities, 
    of my capacity to surmount obstacles, was cornered at last.
\verse Now I was to plunge into the dark, 
    joining that endless procession of sots who had gone on before.
\verse I thought of my poor wife.
\verse There had been much happiness after all.
\verse What would I not give to make amends.
\verse But that was over now.

\verse No words can tell of the loneliness and despair I found 
    in that bitter morass of self-pity.
\verse Quicksand stretched around me in all directions.
\verse I had met my match.
\verse I had been overwhelmed.
\verse Alcohol was my master.

\verse Trembling, I stepped from the hospital a broken man.
\verse Fear sobered me for a bit.
\verse Then came the insidious insanity of that first drink, 
    and on Armistice Day 1934, I was off again.
\verse Everyone became resigned to the certainty that I would have to be shut up somewhere, 
    or would stumble along to a miserable end.
\verse How dark it is before the dawn!
\verse In reality that was the beginning of my last debauch.
\verse I was soon to be catapulted into what I like to call the fourth dimension of existence.
\verse I was to know happiness, peace, and usefulness, 
    in a way of life that is incredibly more wonderful as time passes.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Ebby}
    Near the end of that bleak November, 
    I sat drinking in my kitchen.
\verse With a certain satisfaction I reflected 
    there was enough gin concealed about the house to carry me through that night and the next day.
\verse My wife was at work.
\verse I wondered whether I dared hide a full bottle of gin near the head of our bed.
\verse I would need it before daylight.

\verse My musing was interrupted by the telephone.
\verse The cheery voice of an old school friend asked if he might come over.
\verse He was sober.
\verse It was years since I could remember his coming to New York in that condition.
\verse I was amazed.
\verse Rumor had it that he had been committed for alcoholic insanity.
\verse I wondered how he had escaped.
\verse Of course he would have dinner, 
    and then I could drink openly with him.
\verse Unmindful of his welfare, 
    I thought only of recapturing the spirit of other days.
\verse There was that time we had chartered an airplane to complete a jag!
\verse His coming was an oasis in this dreary desert of futility.
\verse The very thing-an oasis!
\verse Drinkers are like that.

\verse The door opened and he stood there, fresh-skinned and glowing.
\verse There was something about his eyes.
\verse He was inexplicably different.
\verse What had happened?

\verse I pushed a drink across the table.
\verse He refused it.
\verse Disappointed but curious, I wondered what had got into the fellow.
\verse He wasn't himself.

\verse "Come, what's this all about?" I queried.

\verse He looked straight at me.
\verse Simply, but smilingly, he said, "I've got religion."

\verse I was aghast.
\verse So that was it-last summer an alcoholic crackpot; 
    now, I suspected, a little cracked about religion.
\verse He had that starry-eyed look.
\verse Yes, the old boy was on fire all right.
\verse But bless his heart, let him rant!
\verse Besides, my gin would last longer than his preaching.

\verse But he did no ranting.
\verse In a matter of fact way he told how two men had appeared in court, 
    persuading the judge to suspend his commitment.
\verse They had told of a simple religious idea and a practical program of action.
\verse That was two months ago and the result was self-evident.
\verse It worked!

\verse He had come to pass his experience along to me-if I cared to have it.
\verse I was shocked, but interested.
\verse Certainly I was interested.
\verse I had to be, for I was hopeless.

\verse He talked for hours.
\verse Childhood memories rose before me.
\verse I could almost hear the sound of the preacher's voice as I sat, 
    on still Sundays, 
    way over there on the hillside;
    there was that proffered temperance pledge I never signed;
    my grandfather's good natured contempt of some church folk and their doings;
    his insistence that the spheres really had their music;
    but his denial of the preacher's right to tell him how he must listen; 
    his fearlessness as he spoke of these things just before he died; 
    these recollections welled up from the past.
\verse They made me swallow hard.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{There is a Solution}
    That war-time day in old Winchester Cathedral came back again.

\verse I had always believed in a Power greater than myself.
\verse I had often pondered these things.
\verse I was not an atheist.
\verse Few people really are, 
    for that means blind faith in the strange proposition 
    that this universe originated in a cipher and aimlessly rushes nowhere.
\verse My intellectual heroes, the chemists, the astronomers, 
    even the evolutionists, 
    suggested vast laws and forces at work.
\verse Despite contrary indications, 
    I had little doubt that a mighty purpose and rhythm underlay all.
\verse How could there be so much of precise and immutable law, and no intelligence?
\verse I simply had to believe in a Spirit of the Universe, 
    who knew neither time nor limitation.
\verse But that was as far as I had gone.

\verse With ministers, and the world's religions, I parted right there.
\verse When they talked of a God personal to me, 
    who was love, superhuman strength and direction, 
    I became irritated and my mind snapped shut against such a theory.

\verse To Christ I conceded the certainty of a great man, 
    not too closely followed by those who claimed Him.
\verse His moral teaching-most excellent.
\verse For myself, 
    I had adopted those parts which seemed convenient and not too difficult;
    the rest I disregarded.

\verse The wars which had been fought, 
    the burnings and chicanery that religious dispute had facilitated, 
    made me sick.
\verse I honestly doubted whether, on balance, 
    the religions of mankind had done any good.
\verse Judging from what I had seen in Europe and since, 
    the power of God in human affairs was negligible, 
    the Brotherhood of Man a grim jest.
\verse If there was a Devil, he seemed the Boss Universal, 
    and he certainly had me.

\verse But my friend sat before me, 
    and he made the point-blank declaration that 
    God had done for him what he could not do for himself.
\verse His human will had failed.
\verse Doctors had pronounced him incurable.
\verse Society was about to lock him up.
\verse Like myself, he had admitted complete defeat.
\verse Then he had, in effect, been raised from the dead, 
    suddenly taken from the scrap heap 
    to a level of life better than the best he had ever known!

\verse Had this power originated in him?
\verse Obviously it had not.
\verse There had been no more power in him than there was in me at the minute; 
    and this was none at all.

\verse That floored me.
\verse It began to look as though religious people were right after all.
\verse Here was something at work in a human heart which had done the impossible.
\verse My ideas about miracles were drastically revised right then.
\verse Never mind the musty past; 
    here sat a miracle directly across the kitchen table.
\verse He shouted great tidings.

\verse I saw that my friend was much more than inwardly reorganized.
\verse He was on a different footing.
\verse His roots grasped a new soil.

\verse Despite the living example of my friend 
    there remained in me the vestiges of my old prejudice.
\verse The word God still aroused a certain antipathy.
\verse When the thought was expressed that there might be a God personal to me 
    this feeling was intensified.
\verse I didn't like the idea.
\verse I could go for such conceptions as Creative Intelligence, 
    Universal Mind or Spirit of Nature 
    but I resisted the thought of a Czar of the Heavens, 
    however loving His sway might be.
\verse I have since talked with scores of men who felt the same way.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Came to Believe}
    My friend suggested what then seemed a novel idea.  
\verse He said, "Why don't you choose your own conception of God?"

\verse That statement hit me hard.
\verse It melted the icy intellectual mountain 
    in whose shadow I had lived and shivered many years.
\verse I stood in the sunlight at last.

\verse It was only a matter of being willing 
    to believe in a Power greater than myself.
\verse Nothing more was required of me to make my beginning.
\verse I saw that growth could start from that point.
\verse Upon a foundation of complete willingness 
    I might build what I saw in my friend.
\verse Would I have it?
\verse Of course I would!

\verse Thus was I convinced that God is concerned with us humans 
    when we want Him enough.
\verse At long last I saw, I felt, I believed.
\verse Scales of pride and prejudice fell from my eyes.
\verse A new world came into view.

\verse The real significance of my experience in the Cathedral burst upon me.
\verse For a brief moment, I had needed and wanted God.
\verse There had been a humble willingness to have Him with me-and He came.
\verse But soon the sense of His presence had been blotted out by worldly clamors, 
    mostly those within myself.
\verse And so it had been ever since.
\verse How blind I had been.

\verse At the hospital I was separated from alcohol for the last time.
\verse Treatment seemed wise, for I showed signs of delirium tremens.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Turning Over}
    There I humbly offered myself to God, 
    as I then understood Him, 
    to do with me as He would.
\verse I placed myself unreservedly under His care and direction.
\verse I admitted for the first time that of myself I was nothing; 
    that without Him I was lost.
\verse I ruthlessly faced my sins 
    and became willing to have my new-found Friend take them away, 
    root and branch.
\verse I have not had a drink since.

\verse My schoolmate visited me, 
    and I fully acquainted him with my problems and deficiencies.
\verse We made a list of people I had hurt 
    or toward whom I felt resentment.
\verse I expressed my entire willingness to approach these individuals, 
    admitting my wrong.
\verse Never was I to be critical of them.
\verse I was to right all such matters to the utmost of my ability.

\verse I was to test my thinking by the new God-consciousness within.
\verse Common sense would thus become uncommon sense.
\verse I was to sit quietly when in doubt, 
    asking only for direction and strength to meet my problems as He would have me.
\verse Never was I to pray for myself, 
    except as my requests bore on my usefulness to others.
\verse Then only might I expect to receive.
\verse But that would be in great measure.

\verse My friend promised when these things were done 
    I would enter upon a new relationship with my Creator; 
    that I would have the elements of a way of living 
    which answered all my problems.
\verse Belief in the power of God, 
    plus enough willingness, honesty and humility 
    to establish and maintain the new order of things, 
    were the essential requirements.

\verse Simple, but not easy; 
    a price had to be paid.
\verse It meant destruction of self-centeredness.
\verse I must turn in all things to the Father of Light 
    who presides over us all.

\verse These were revolutionary and drastic proposals, 
    but the moment I fully accepted them, 
    the effect was electric.
\verse There was a sense of victory, 
    followed by such a peace and serenity as I had never known.
\verse There was utter confidence.
\verse I felt lifted up, 
    as though the great clean wind of a mountain top blew through and through.
\verse God comes to most men gradually, 
    but His impact on me was sudden and profound.

\verse For a moment I was alarmed, and called my friend, the doctor, 
    to ask if I were still sane.
\verse He listened in wonder as I talked.

\verse Finally he shook his head saying,
    \begin{quote}
    "Something has happened to you I don't understand.
    But you had better hang on to it.
    Anything is better than the way you were."
    \end{quote}
\verse The good doctor now sees many men who have such experiences.
\verse He knows that they are real.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Carry Forth}
    While I lay in the hospital 
    the thought came that there were thousands of hopeless alcoholics 
    who might be glad to have what had been so freely given me.
\verse Perhaps I could help some of them.
\verse They in turn might work with others.

\verse My friend had emphasized the absolute necessity 
    of demonstrating these principles in all my affairs.
\verse Particularly was it imperative to work with others 
    as he had worked with me.
\verse Faith without works was dead, he said.
\verse And how appallingly true for the alcoholic!
\verse For if an alcoholic failed to perfect and enlarge his spiritual life 
    through work and self-sacrifice for others, 
    he could not survive the certain trials and low spots ahead.
\verse If he did not work, 
    he would surely drink again, 
    and if he drank, 
    he would surely die.
\verse Then faith would be dead indeed.
\verse With us it is just like that.

\verse My wife and I abandoned ourselves with enthusiasm 
    to the idea of helping other alcoholics 
    to a solution of their problems.
\verse It was fortunate, 
    for my old business associates remained skeptical for a year and a half, 
    during which I found little work.
\verse I was not too well at the time, 
    and was plagued by waves of self-pity and resentment.
\verse This sometimes nearly drove me back to drink, 
    but I soon found that when all other measures failed, 
    work with another alcoholic would save the day.
\verse Many times I have gone to my old hospital in despair.
\verse On talking to a man there, 
    I would be amazingly lifted up and set on my feet.
\verse It is a design for living that works in rough going.

\verse We commenced to make many fast friends 
    and a fellowship has grown up among us 
    of which it is a wonderful thing to feel a part.
\verse The joy of living we really have, 
    even under pressure and difficulty.
\verse I have seen hundreds of families set their feet 
    in the path that really goes somewhere; 
    have seen the most impossible domestic situations righted; 
    feuds and bitterness of all sorts wiped out.  
\verse I have seen men come out of asylums 
    and resume a vital place in the lives of their families and communities.  
\verse Business and professional men have regained their standing.  
\verse There is scarcely any form of trouble and misery 
    which has not been overcome among us.  
\verse In one western city and its environs 
    there are one thousand of us and our families.  
\verse We meet frequently so that newcomers may find the fellowship they seek.  
\verse At these informal gatherings one may often see from 50 to 200 persons.  
\verse We are growing in numbers and power.

\verse An alcoholic in his cups is an unlovely creature.  
\verse Our struggles with them are variously strenuous, comic, and tragic.  
\verse One poor chap committed suicide in my home.  
\verse He could not, or would not, see our way of life.

\verse There is, however a vast amount of fun about it all.  
\verse I suppose some would be shocked at our seeming worldliness and levity.  
\verse But just underneath there is deadly earnestness.  
\verse Faith has to work twenty-four hours a day in and through us, or we perish.

\verse Most of us feel we need look no further for Utopia.  
\verse We have it with us right here and now.  
\verse Each day my friend's simple talk in our kitchen multiplies itself 
    in a widening circle of peace on earth and good will to men.
\end{biblechapter}

