\biblebook{Earl} %\biblebook{Physician}

\bbHeading{BB. PHYSICIAN, HEAL THYSELF!}
\bbChapterPreamble


\begin{biblechapter}
\verseWithHeading{Foreword}
    Psychiatrist and surgeon, 
    he had lost his way until
    he realized that God, 
    not he, 
    was the Great Healer.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Skid Row Of Success}
    I AM A PHYSICIAN, 
    licensed to practice in a western state.
\verse I am also an alcoholic.
\verse In two ways I may be a little different from other alcoholics.
\verse First, we all hear at A.A. meetings 
    about those who have lost everything, 
    those who have been in jail, 
    those who have been in prison, 
    those who have lost their families, 
    those who have lost their income.
\verse I never lost any of it.
\verse I never was on skid row.
\verse I made more money the last year of my drinking 
    than I ever made before in my whole life.
\verse My wife never hinted that she would leave me.
\verse Everything that I touched from grammar school on was successful.
\verse I was president of my grammar school student body.
\verse I was president of all my classes in high school 
    and in my last year I was president of that student body.
\verse I was president of each class in the University, 
    and president of that student body.
\verse I was voted the man most likely to succeed.
\verse The same thing occurred in medical school.
\verse I belong to more medical societies and honor societies 
    than men ten to twenty years my senior.

\verse Mine was the skid row of success.
\verse The physical skid row in any city is miserable.
\verse The skid row of success is just as miserable.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Tastes Good}
\verse The second way in which, perhaps, 
    I differ from some other alcoholics is this;
    many alcoholics state that 
    they didn’t particularly like the taste of alcohol, 
    but that they liked the effect.
\verse I loved alcohol!
\verse I used to like to get it on my fingers 
    so I could lick them and get another taste.
\verse I had a lot of fun drinking.
\verse I enjoyed it immensely.
\verse And then one ill-defined day, 
    one day that I can’t recall, 
    I stepped across the line that alcoholics know so well, 
    and from that day on drinking was miserable.
\verse When a few drinks made me feel good 
    before I went over that line, 
    those same drinks now made me wretched.
\verse In an attempt to get over that feeling, 
    there was a quick onslaught of a greater number of drinks, 
    and then all was lost.
\verse Alcohol failed to serve the purpose.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{The Last One}
\verse On the last day I was drinking 
    I went up to see a friend 
    who had had a good deal of trouble with alcohol, 
    and whose wife had left him a number of times.
\verse He had come back, however, 
    and he was on this program.
\verse In my stupid way I went up to see him 
    with the idea in the back of my mind that 
    I would investigate Alcoholics Anonymous 
    from a medical standpoint.
\verse Deep in my heart was the feeling that 
    maybe I could get some help here.
\verse This friend gave me a pamphlet, 
    and I took it home and had my wife read it to me.
\verse There were two sentences in it that struck me.
\verse One said, 
    “Don’t feel that you are a martyr because you stopped drinking,” 
    and this hit me between the eyes.
\verse The second one said, 
    “Don’t feel that you stop drinking for anyone other than yourself,” 
    and this hit me between the eyes.
\verse After my wife had read this to me, 
    I said to her, as I had said many times in desperation, 
    “I have got to do something.”
\verse She’s a good-natured soul and said, 
    “I wouldn’t worry about it; probably something will happen.”
\verse And then we went up the side of a hill 
    where we have a little barbeque area 
    to make the fire for the barbecue, 
    and on the way up, 
    I thought to myself—I’ll go back down to the kitchen 
    and refill this drink.
\verse And just then something did happen.

\verse The thought came to me— This is the last one!
\verse I was well into the second fifth by this time.
\verse And as that thought came to me, 
    it was as though someone had reached down 
    and taken a heavy overcoat off my shoulders, 
    for that was the last one.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Twelth Step}
\verse About two days later I was called by a friend of mine 
    from Nevada City—he’s a brother of my wife’s closest friend.
\verse He said, “Earl?” and I said, “Yes.”
\verse He said, “I’m an alcoholic, what do I do?”
\verse And I gave him some idea of what you do, 
    and so I made my first Twelfth Step call 
    before I ever came into the program.
\verse The satisfaction I got 
    from giving him a little of what I had read in those pamphlets 
    far surpassed 
    any feeling that I had ever had before in helping patients.
\end{biblechapter}


\begin{biblechapter}
\verseWithHeading{Meetings}
\verse So I decided that I would go to my first meeting.
\verse I was introduced as a psychiatrist.
\verse (I belong to the American Psychiatric Society, 
    but I don’t practice psychiatry as such.
    I am a surgeon.)

\verse As someone in A.A. said to me once upon a time, 
    there is nothing worse than a confused psychiatrist.

\verse I will never forget the first meeting that I attended.
\verse There were five people present, including myself.
\verse At one end of the table sat our community butcher.
\verse At the other side of the table 
    sat one of the carpenters in our community, 
    and at the further end of the table sat the man who ran the bakery, 
    while on one side sat my friend who was a mechanic.
\verse I recall, as I walked into that meeting, saying to myself, 
    “Here I am, a Fellow of the American College of Surgeons, 
    a Fellow of the International College of Surgeons, 
    a diplomat of one of the great specialty boards in these United States, 
    a member of the American Psychiatric Society, 
    and I have to go to the butcher, 
    the baker and the carpenter 
    to help make a man out of me!”

\verse Something else happened to me.
\verse This was such a new thought that 
    I got all sorts of books on Higher Powers, 
    and I put a Bible by my bedside, 
    and I put a Bible in my car.
\verse It is still there.
\verse And I put a Bible in my locker at the hospital.
\verse And I put a Bible in my desk.
\verse And I put a Big Book by my night stand, 
    and I put a “Twelve Steps and Twelve Traditions” 
    in my locker at the hospital, 
    and I got books by Emmet Fox, 
    and I got books by God-knows-who, 
    and I got to reading all these things.
\verse And the first thing you know 
    I was lifted right out of the A.A. group, 
    and I floated higher, and higher, and even higher, 
    until I was way up on a pink cloud which is known as Pink Seven, 
    and I felt miserable again.
\verse So I thought to myself, 
    I might just as well be drunk as feel like this.

\verse I went to Clark, the community butcher, and I said, 
    “Clark, what is the matter with me? 
\verse I don’t feel right.
\verse I have been on this program for three months and I feel terrible.”
\verse And he said, “Earl, 
    why don’t you come on over and let me talk to you for a minute.”
\verse So he got me a cup of coffee, and a piece of cake, 
    and sat me down and said, 
    “Why, there’s nothing wrong with you.
\verse You’ve been sober for three months, been working hard.
\verse You’ve been doing all right.”
\verse But then he said, 
    “Let me say something to you.
\verse We have here in this community an organization which helps people,
    and this organization is known as Alcoholics Anonymous.
\verse Why don’t you join it?”
\verse I said, “What do you think I’ve been doing?”
\verse “Well,” he said, 
    “you’ve been sober, 
    but you’ve been floating way up on a cloud somewhere.
\verse Why don’t you go home and get the Big Book 
    and open it at page seventy and see what it says?”
\verse So I did.
\verse I got the Big Book and I read it, 
    and this is what it said: 
    “Rarely have we seen a person fail 
    who has thoroughly followed our path.”
\verse The word “thoroughly” rang a bell.
\verse And then it went on to say: 
    “Half measures availed us nothing.
\verse We stood at the turning point.”
\verse And the last sentence was 
    “We asked His protection and care with complete abandon.”

\verse “Complete abandon”; 
    “Half measures availed us nothing”; 
    “Thoroughly follow our path”; 
    “Completely give oneself to this simple program”—rang 
    in my swelled head.

\verse In 1935, as a physician, 
    I went into psychoanalysis to get relief.
\verse I spent five and a half years in psychoanalysis 
    and proceeded to become a drunk.
\verse I don’t mean that in any sense as a 
    derogatory statement about psychotherapy; 
    it’s a very great tool, not too potent, but a great tool.
\verse I would do it again.

\verse I tried every gimmick that there was to get some peace of mind, 
    but it was not until I was brought to my alcoholic knees, 
    when I was brought to a group in my own community 
    with the butcher, the baker, the carpenter and the mechanic, 
    who were able to give me the Twelve Steps, 
    that I was finally given some semblance of an answer 
    to the last half of the First Step.
\verse So, after taking the first half of the First Step, 
    and very gingerly admitting myself to Alcoholics Anonymous, 
    something happened.
\verse And then I thought to myself: 
    “Imagine an alcoholic admitting anything!”
\verse But I made my admission just the same.

\verse The Third Step said: 
    “Made a decision to turn our will 
    and our lives over to the care of God 
    as we understood Him.”
\verse Now they asked us to make a decision!
\verse We’ve got to turn the whole business over 
    to some joker we can’t even see!
\verse And this chokes the alcoholic.
\verse Here he is powerless, unmanageable, 
    in the grip of something bigger than he is, 
    and he’s got to turn the whole business over to someone else!
\verse It fills the alcoholic with rage.
\verse We are great people.
\verse We can handle anything.
\verse And so one gets to thinking to oneself, 
    “Who is this God?
\verse Who is this fellow we are supposed to turn everything over to?
\verse What can He do for us that we can’t do for ourselves?”
\verse Well, I don’t know who He is, but I’ve got my own idea.

\verse For myself, 
    I have an absolute proof of the existence of God.
\verse I was sitting in my office 
    one time after I had operated on a woman.
\verse It was a long four or five hour operation, 
    a large surgical procedure, 
    and she was on her ninth or tenth post-operative day.
\verse She was doing fine, she was up and around, 
    and that day her husband phoned me and said, 
    “Doctor, thanks very much for curing my wife,” 
    and I thanked him for his felicitations, and he hung up.
\verse And then I scratched my head, and said to myself, 
    “What a fantastic thing for a man to say, 
    that I cured his wife.
\verse Here I am down at my office behind my desk 
    and there she is out at the hospital.
\verse I am not even there, 
    and if I was there the only thing I could do 
    would be to give her moral support, 
    and yet he thanks me for curing his wife.”
\verse I thought to myself—what is curing that woman?
\verse Yes, I put in those stitches.
\verse The Great Boss had given me diagnostic and surgical talent, 
    and He has loaned it to me to use for the rest of my life.
\verse It doesn’t belong to me.
\verse He has loaned it to me and I did my job, 
    but that ended nine days ago.
\verse What healed those tissues, 
    those tissues that I closed, 
    what healed them?
\verse I didn’t.
\verse This to me is the proof 
    of the existence of a Somethingness greater than I am.
\verse I couldn’t practice medicine without the Great Physician.
\verse All I do in a very simple way, 
    is to help Him cure my patients.

\verse Shortly after I was starting to work on the program 
    I realized that I was not a good father; 
    I wasn’t a good husband, 
    but, oh, I was a good provider.
\verse I never robbed my family of anything.
\verse I gave them everything, 
    except the greatest thing in the world, 
    and that is peace of mind.
\verse So I went to my wife and asked her, 
    wasn’t there something 
    that she and I could do to somehow get together, 
    and she turned on her heel and looked me squarely in the eye, 
    and said, 
    “You don’t care anything about my problem,” 
    and I could have smacked her, but I said to myself, 
    “Grab on to your serenity!”

\verse She left, and I sat down and crossed my hands, 
    and looked up and said, 
    “For God’s sake, help me.”
\verse And then a silly, simple thought came to me.
\verse I didn’t know anything about being a father; 
    I don’t know how to come home 
    and work week-ends like other husbands; 
    I don’t know how to entertain my family.
\verse But I remembered that every night after dinner 
    my wife would get up and do the dishes.
\verse Well, I could do the dishes.
\verse So I went to her and said, 
    “There’s only one thing I want in my whole life, 
    and I don’t want any commendation; 
    I don’t want any credit; 
    I don’t want anything from you or Janey 
    for the rest of your life except one thing; 
    and that is, the opportunity to do anything you want always, 
    and I would like to start off by doing the dishes.” 
\verse And now I am doing the darn dishes every night!

\verse Doctors have been notoriously unsuccessful in helping alcoholics.
\verse They have contributed 
    fantastic amounts of time and work to our problem, 
    but they aren’t able, it seems, 
    to arrest either your alcoholism or mine.

\verse And the clergy have tried hard to help us, 
    but we haven’t been helped.
\verse And the psychiatrist has had thousands of couches, 
    and has put you and me on them many, many times, 
    but he hasn’t helped us very much, 
    though he has tried hard; 
    and we owe the clergy and the doctor and the psychiatrist 
    a deep debt of gratitude, 
    but they haven’t helped our alcoholism, 
    except in a rare few instances.
\verse But—Alcoholics Anonymous has helped.

\verse What is this power that A.A. possesses?
\verse This curative power?
\verse I don’t know what it is.
\verse I suppose the doctor might say,
    “This is psychosomatic medicine.”
\verse I suppose the psychiatrist might say, 
    “This is benevolent interpersonal relations.”
\verse I suppose others would say, 
    “This is group psychotherapy.”

\verse To me it is God.
\end{biblechapter}
