\biblebook{1 Foreword}

\bbChapterPreamble

\bbHeading{FOREWORD TO FIRST ADDITION p. xiii-xiv}

\begin{biblechapter}
\verseWithHeading{First Ed} \begin{centering}\emph{
    This is the Foreword as it appeared in the first 
    printing of the first edition in 1939.
}
\end{centering}

\verseWithHeading{Program of Attraction} 
    WE, OF Alcoholics Anonymous, 
    are more than one hundred men and women 
    who have recovered from a seemingly hopeless state 
    of mind and body. 
\verse To show other alcoholics precisely how we have recovered 
    is the main purpose of this book. 
\verse For them, we hope these pages will prove so convincing 
    that no further authentication will be necessary. 
\verse We think this account of our experiences will help everyone 
    to better understand the alcoholic. 
\verse Many do not comprehend that the alcoholic is a very sick person.
\verse And besides, 
    we are sure that our way of living has its advantages for all. 

\verseWithHeading{Anonymity \& Avocation}
    It is important that we remain anonymous 
    because we are too few, at present 
    to handle the overwhelming number of personal appeals 
    which may result from this publication. 
\verse Being mostly business or professional folk, 
    we could not well carry on our occupations in such an event. 
\verse We would like it understood that our alcoholic work is an avocation. 

\verse When writing or speaking publicly about alcoholism, 
    we urge each of our Fellowship to omit his personal name, 
    designating himself instead as 
    “a member of Alcoholics Anonymous.”

\verseWithHeading{Anonymity \& Press}
    Very earnestly we ask the press also, 
    to observe this request, 
    for otherwise we shall be greatly handicapped.

\verseWithHeading{Preamble}
    We are not an organization in the conventional sense of the word.
\verse There are no fees or dues whatsoever. 
\verse The only requirement for membership is an honest desire to stop drinking. 
\verse We are not allied with any particular faith, sect or denomination, 
    nor do we oppose anyone.
\verse We simply wish to be helpful to those who are afflicted. 

\verseWithHeading{Grapevine}
    We shall be interested to hear from those 
    who are getting results from this book, 
    particularly from those who have commenced work with other alcoholics.
\verse We should like to be helpful to such cases. 

\verse Inquiry by scientific, medical, and religious societies 
    will be welcomed. 

\verse ALCOHOLICS ANONYMOUS
\end{biblechapter}

