\biblebook{2 Preface}

Extract from Alcoholics Anonymous 2nd Ed.,© AA World Services, Inc., 
    used here for scholarly analysis and commentary.
The B.B. 2nd Ed. 'Preface', p. xi-xii


\begin{biblechapter}
\verseWithHeading{Preface}
   THIS IS the second edition of the book "Alcoholics Anonymous," 
   which made its first appearance in April 1939.
\verse More than 300,000 copies of the first edition are now in circulation.
\verse Because this book has become 
    the basic text for our Society 
    and has helped such large numbers 
    of alcoholic men and women to recovery, 
    there exists a sentiment against any radical changes being made in it.
\verse Therefore, the first portion of this volume, 
    describing the A.A. recovery program, 
    has been left largely untouched.

\verseWithHeading{Changes}
    But the personal history section has been considerably revised 
    and enlarged
    in order to present a more accurate representation of 
    our membership as it is today.
\verse When the book was first printed, 
    we had scarcely 100 members all told, 
    and every one of them was an almost hopeless case of alcoholism. 
\verse This has changed.
\verse A.A. now helps alcoholics in all stages of the disease.
\verse It reaches into every level of life 
    and into nearly all occupations.
\verse Our membership now includes many young people.
\verse Women, who were at first very reluctant to approach A.A., 
    have come forward in large numbers.
\verse Therefore the range of the story section has been broadened 
    so that every alcoholic reader may find a reflection 
    of him or herself in it.

\verse As a souvenir of our past, 
    the original Foreword has been preserved 
    and is followed by a second 
    on describing Alcoholics Anonymous of 1955.

\verseWithHeading{Endorsements}
   Following the Forewords, 
   there appears a section called "The Doctor's Opinion."  
   This also has been kept intact, 
   just as it was originally written in 1939 
   by the late Dr. William D. Silkworth, 
   our Society's great medical benefactor. 
\verse Besides Dr. Silkworth's original statement, 
    there have been added, 
    in the Appendices,
    a number of the medical and religious endorsements
    which have come to us in recent years.

\verseWithHeading{Contact}
    On the last pages of this second edition 
    will be found the Twelve Traditions of Alcoholics Anonymous, 
    the principles upon which our A.A. groups function, 
    together with the directions for getting in touch with A.A.
